RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-06-24 manuscripts/manuscript.Rmd
removed redundant 'also'
expanded a bit more on the problems with names-based data integration

`RNeXML` also provides various functions to assist in automatically adding
other more specific metadata to various elements of the NeXML data.
One common use case is that of taxonomic identifers.  Misspellings or
inconsistent use of taxonomic names in phylogenetic data are a common
source of frustration in reusing phylogenetic trees. By associating the
taxonomic labels against a specific, centralized database we can catch
typographical errors and indicate more precisely which classification
we are appealing to in the event of conflicting taxonomic definitions.
In this example, we indicate that we intend the bird orders listed in
the tree to correspond to the NCBI definitions

>>>>

`RNeXML` provides various functions to assist in automatically adding
other more specific metadata to various elements of the NeXML data.
One common use case is that of taxonomic identifers.  Misspellings or
inconsistent use of taxonomic names in phylogenetic data are a common
source of frustration in reusing phylogenetic trees, especially when 
integrating data from different sources: trees might come from one place
that uses one taxonomy, character data and occurrence data might come from
other places that use different taxonomies. Hence, not just misspellings, 
but also synonyms, homonyms and incompatible taxon concepts might plague
the end user. By associating the
taxonomic labels against a specific, centralized database we can catch
some of these inconsistencies and indicate more precisely which classification
we are appealing to in the event of conflicting taxonomic definitions.
In this example, we indicate that we intend the bird orders listed in
the tree to correspond to the NCBI definitions
